---
title: "Introduction to StatComp21089"
author: "Dai Jun"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21089}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

GradientDescent function is the R code implementation of gradient descent method in numerical analysis. If stepmethod=True,function uses backward descent method to find the step length,else uses fixed step.
The purpose of GnS is to select T_n in a set of response variables with a double-truncated function variable data.

## Benchmarking

```{r}
GradientDescent<-function(x,y,error,maxiter,stepmethod=T,step=0.001,alpha=0.25,beta=0.8)
{
  m<-nrow(x)
  x<-cbind(matrix(1,m,1),x)
  n<-ncol(x)
  theta<-matrix(rep(0,n),n,1)  #theta initial value is set to 0
  iter<-1
  newerror<-1
  
  while((newerror>error)|(iter<maxiter)){
    iter<-iter+1
    h<-x%*%theta  
    des<-t(t(h-y)%*%x)  #gradient
    #Backward descent method to find the step length t
    if(stepmethod==T){
      sstep=1
      new_theta<-theta-sstep*des
      new_h<-x%*%new_theta
      costfunction<-t(h-y)%*%(h-y)  #Least squares loss function
      new_costfunction<-t(new_h-y)%*%(new_h-y)
      #Backward descent method to find the step length sstep
      while(new_costfunction>costfunction-alpha*sstep*sum(des*des)){
        sstep<-sstep*beta
        new_theta<-theta-sstep*des
        new_h<-x%*%new_theta
        new_costfunction<-t(new_h-y)%*%(new_h-y)  
      }
      newerror<-t(theta-new_theta)%*%(theta-new_theta)       
      theta<-new_theta     
    }
    
    #Set fixed step directly
    if(stepmethod==F){        
      new_theta<-theta-step*des
      new_h<-x%*%new_theta
      # new_costfunction<-t(new_h-y)%*%(new_h-y)
      newerror<-t(theta-new_theta)%*%(theta-new_theta)
      theta<-new_theta 
    }
    
  }
  costfunction<-t(x%*%theta-y)%*%(x%*%theta-y)
  result<-list(theta,iter,costfunction)
  names(result)<-c('coefficient','iter','error')
  result
}
```

GnS() is a function that handles the effects of truncation data.

```{r,eval=FALSE}
GnS=function(x)    # x=(Y,U,V)
{
  n<- nrow(x)
  H<- h1<- h2<- F<- f<- 1:n
  I=function(t)
  {
    if(t[2]<=t[1]&t[1]<=t[3]) {return(1)}
    else {return(0)}
  }
  for(i in 1:n) {h1[i]<- 1/n}
  for(i in 1:n)
  {
    H[i]<- 0
    for(j in 1:n) {H[i]<- H[i]+h1[j]*I(c(x[j,1],x[i,2],x[i,3]))}
  }
  while(abs(max(h1-h2))>=10^(-6))
  {
    h2<- h1
    for(j in 1:n)
    {
      f[j]<- 0
      for(i in 1:n){f[j]<- f[j]+1/H[i]}
      f[j]<- (1/f[j])*(1/H[j])
    }
    for(i in 1:n)
    {
      F[i]<- 0
      for(j in 1:n){F[i]<- F[i]+f[j]*I(c(x[i,1],x[j,2],x[j,3]))}
    }
    for(j in 1:n)
    {
      h1[j]<- 0
      for(i in 1:n) {h1[j]<- h1[j]+1/F[i]}
      h1[j]<- (1/h1[j])*(1/F[j])
    }
    for(i in 1:n)
    {
      H[i]<- 0
      for(j in 1:n) {H[i]<- H[i]+h1[j]*I(c(x[j,1],x[i,2],x[i,3]))}
    }
  }
  return(f)
}
```